\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[purple]{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Alex}
\familyname{Denisov}
\address{}{Berlin, Germany}
\mobile{+49 152 06077867}
\email{1101.debian@gmail.com}
\homepage{https://lowlevelbits.org}
\extrainfo{Software should be beautiful. Both inside and outside.}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
\maketitle

\section{Projects}
  \subsection{Commercial Projects}
  \cvline
    {Uberchord}
    {\url{https://itunes.apple.com/US/app/id952669753}\newline{}
    \textbf{Your personal guitar trainer.}\newline{}
    Introducing various testing techniques to improve quality of the code base and improve maintainability.}
  \cvline
    {Blacklane}
    {\url{https://itunes.apple.com/us/app/blacklane/id524123600}\newline{}
    \textbf{Client app for the Blacklane customers.}\newline{}
    Introduced Unit Testing.\newline{}
    Implemented event tracking to understand the users better.\newline{}
    Constantly improving maintainability of the code base.}
  \cvline
    {Talendo}
    {\url{https://itunes.apple.com/us/app/talendo-jobborse-und-stellen/id763634231}\newline{}
    \textbf{Job-search portal for German market.}\newline{}
    Helped a designer to improve mockups and overall user-flow.\newline{}
    Developed API specifications for backend team.\newline{}
    Developed the app from a proof of concept to the AppStore.\newline{}
    Set up beta testing via Enterprise Distribution.}
  \subsection{OpenSource Projects}
  \cvline
    {Clang}
    {\url{http://clang.llvm.org}\newline{}
    \textbf{C/C++/Objective-C compiler.}\newline{}
    Extended Objective-C's boxed expressions to accept C structures and unions.\newline{}
    Implemented new warning for Objective-C.\newline{}
    Fixed couple of bugs.\newline{}
    Committer since Feb, 2015.\newline{}
    My contribution:\newline{}
    \url{https://github.com/llvm-mirror/clang/commits?author=AlexDenisov}
    }
  \cvline
    {Mull}
    {\url{https://github.com/mull-project/mull}\newline{}
    \textbf{LLVM-based mutation testing system.}\newline{}
    Currently it supports C++ and GoogleTest.\newline{}
    Here is the idea explained:\newline{}
    \url{https://lowlevelbits.org/llvm-based-mutation-testing-system/}
    }
  \cvline
    {Components}
    {\url{https://github.com/AlexDenisov/Components}\newline{}
    \textbf{Makefile-based approach to manage dependencies.}\newline{}
    \url{https://lowlevelbits.org/components-management/}
    }
\pagebreak
\section{Experience}
\cventry
  {Jul 2016 - Dec, 2017}
  {Software developer}
  {Uberchord, Berlin, Germany}
  {\newline{}\url{https://www.uberchord.com}}{}
  {Maintaining existing app: implementing new features, fixing bugs.}
\cventry
  {Sep 2014 - Jun 2016}
  {Software developer}
  {Blacklane, Berlin, Germany}
  {\newline{}\url{https://blacklane.com}}{}
  {Maintaining existing apps: implementing new features, fixing bugs.}
\cventry
  {May 2013 - Aug 2014}
  {Software engineer}
  {Railsware, Kiev, Ukraine}
  {\newline{}\url{http://railsware.com}}{}
  {Assessment of requirements for software development and time estimation.\newline{}
  Taught backend developers how to write iOS apps and learned from backend developers how to write backends.}
\cventry
  {Oct 2012 - Mar 2013}
  {iOS developer}
  {Stanfy LLC. Kiev, Ukraine}
  {\newline{}\url{http://stanfy.com}}{}
  {Assessment of requirements for software development and time estimation.
  \newline{}Software development.}
\cventry
  {Feb 2011 - Oct 2012}
  {iOS/RubyOnRails developer}
  {MLSDev LLC. Donetsk, Ukraine}
  {\newline{}\url{http://mlsdev.com}}{}
  {Assessment of requirements for software development and time estimation.\newline{}
  Software development. Web-services deployment and support.}
\cventry
  {Aug 2010 - Feb 2011}
  {C++/Qt developer}
  {WiseTroll (Sole Proprietorship). Donetsk, Ukraine}
  {}{}
  {Assessment of requirements for software development and time estimation.
  \newline{}Software development.}

\section{Technical Skills}
\cvline
  {Languages}{Objective-C, C++, Swift, Bash, Ruby, JS}
\cvline
  {VCS}{Git, SVN, Mercurial}
\cvline
  {OS}{OS X, Linux (Debian), FreeBSD}
\cvline
  {Techniques}{TDD, XP, Scrum, Kanban}

\section{Education}
  \subsection{University}
  \cventry
    {Oct 2006 - Dec 2011}
    {Software Development}
    {Computer Academy "Step", Donetsk, Ukraine}
    {}{}
    {Team member, represented Ukraine at the final of ImagineCup'10 at Poland.}
  \cventry
    {Sep 2006 - Jul 2010}
    {Management of Organizations, Bachelor}
    {Open International University of Human Development "Ukraine"}
    {}{}{}
  \subsection{MOOCs (Coursera)}
  \cventry
    {Sep 2015 - Nov 2015}
    {Automata}
    {\newline Learned a lot about automata, regular languages, grammars \&c.}
    {}{\newline\url{https://www.coursera.org/course/automata}}{}
  \cventry
    {Apr 2015 - Jun 2015}
    {From Nand to Tetris / Part I}
    {\newline Learned basics of logic circuits. Implemented Assembler for a 'toy' machine}
    {}{\newline\url{https://www.coursera.org/course/nand2tetris1}}{}
  \cventry
    {Sep 2014 - Nov 2014}
    {Functional Programming Principles in Scala}
    {\newline Learned basics of functional programming}
    {}{\newline\url{https://www.coursera.org/course/progfun}}{}

\section{Public Activity}
  \subsection{Speaking}
  \cventry
    {FOSDEM 2017}
    {Mutation Testing: Leaving the stone age}
    {}
    {}{}
    {Link: \url{https://fosdem.org/2017/schedule/event/mutation_testing/}}
  \cventry
    {RIT++ 2016}
    {Getting started with LLVM using Swift}
    {}
    {}{}
    {Link: \url{http://appsconf.ru/2016/abstracts/2165}}
  \cventry
    {FOSDEM 2016}
    {How to use LLVM C API with Swift}
    {}
    {}{}
    {Link: \url{https://fosdem.org/2016/schedule/event/llvm_c_swift/}}
  \cventry
    {Mobile Warsaw}
    {Magic Behind Xcode}
    {Compilation}
    {}{}
    {Slides: \url{https://speakerdeck.com/alexdenisov/magic-behind-xcode}}
  \cventry
    {CocoaHeads Berlin}
    {Compilation Process}
    {How a program is born}
    {}{}
    {Slides: \url{https://speakerdeck.com/alexdenisov/compilation-process}}
  \cventry
    {CocoaHeads Berlin}
    {BloodMagic}
    {Custom property attributes for Objective-C}
    {}{}
    {Slides: \url{https://speakerdeck.com/alexdenisov/bloodmagic}}
  \subsection{On the Internet}
    \cvline{Blog}{\url{https://lowlevelbits.org}}
    \cvline{Blog}{\url{https://systemundertest.org}}
    \cvline{GitHub}{\url{https://github.com/AlexDenisov}}
    \cvline{StackOverflow}{\url{http://stackoverflow.com/users/829116/alexdenisov}}
    \cvline{LinkedIn}{\url{http://www.linkedin.com/pub/alexey-denisov/2a/bab/a29}}

\end{document}
